Inference methods comparison for the simplified Naomi model

### 2023-04-27 src/naomi-simple_ks/ks.Rmd
Rename "compare" to "ks" in preparation for more different types of posterior comparisons

  **Task** In this report, we compare the accuracy of the posterior distributions obtained from these inference methods using histograms, Kolmogorov-Smirnov tests, maximum mean discrepancy and Pareto-smoothed importance sampling.
---

>>>>

  **Task** In this report, we compare the accuracy of the posterior distributions obtained from these inference methods using histograms and Kolmogorov-Smirnov tests.
---
